\section{Introduction}
\label{sec:introduction}

Global assets under management have reached unprecedented levels, exceeding USD 128 trillion in 2024, with a substantial share allocated to delegated investment vehicles such as mutual funds, hedge funds, and institutional mandates.\footnote{\url{https://web-assets.bcg.com/cc/0a/25876ea740168e908a8652e147d7/2025-gam-report-april-2025.pdf}; \url{https://www.pwc.com/ng/en/press-room/global-assets-under-management-set-to-rise.html}} In these settings, investors delegate portfolio decisions to professional managers while retaining only limited control over the underlying investment process. Unlike direct ownership of firms, where investors may exercise governance rights, delegated portfolio management typically involves contracts that specify outcomes rather than actions. As a result, investors have little influence over how risk is chosen or implemented, and managerial decisions are only imperfectly observable \citep{BebchukCohenHirst2017}.

This institutional structure creates scope for agency frictions. Managers are compensated primarily through fees linked to assets under management, while investors care about risk-adjusted returns as well. Empirical evidence further indicates that fees are not necessarily aligned with performance, as poorly performing funds may charge higher fees than better-performing peers \citep{Gil-Bazo2008}. At the same time, investor capital flows respond asymmetrically to performance. A large literature documents that inflows increase strongly with good performance, particularly in the upper tail of the return distribution, while outflows following poor performance are more gradual \citep{Ippolito1992ConsumerReaction, chevalier1997risk, sirri1998costly}. This convex flow--performance relationship implies that the mapping from performance to assets under management is nonlinear.

The interaction between fee structures and convex flows has important implications for managerial incentives. Because fees are proportional to assets under management, and assets respond disproportionately to strong performance, the manager's payoff becomes convex in returns. This convexity resembles the payoff of a financial option. As in standard option pricing, higher volatility increases the probability of extreme positive outcomes, which are disproportionately rewarded through inflows. Consequently, even when expected returns per unit of risk are unchanged, a manager can increase expected compensation by raising portfolio volatility \citep{BrownHarlowStarks1996}. This creates a divergence between the manager's privately optimal choice of risk and the level of risk preferred by investors.

The central objective of this paper is to characterize how compensation contracts can be designed to mitigate this risk-shifting incentive. We develop a tractable principal--agent model of delegated portfolio management in which the manager chooses portfolio volatility and investors allocate capital based on realized performance. The model incorporates a convex flow--performance relationship and a fee structure tied to assets under management. Within this framework, we derive the incentive-compatible contract that implements a target level of portfolio volatility chosen by the investor.

Our main result is that, under mild conditions, there exists a unique fee schedule that aligns the manager's incentives with the investor's desired risk target. This incentive-compatible fee can be expressed as a function of the target volatility. Furthermore, we show that over empirically relevant ranges, this relationship can be well approximated by a simple affine function. This yields a contract that can be interpreted as compensating the manager for the level of risk undertaken rather than for realized outcomes. We refer to this structure as a ``pay for risk, not luck'' framework. A numerical calibration based on empirical parameter values demonstrates that the linear approximation closely tracks the optimal contract and provides a practical representation of the underlying incentive structure.

This paper contributes to the literature on agency problems in delegated portfolio management. In classic principal--agent models, investors contract on observable outcomes because effort and information acquisition are not directly observable \citep{Holmstrom1979, AdmatiPfleiderer1997}. This gives rise to well-known distortions, including underinvestment in costly effort, short-horizon behavior around evaluation dates, and actions that increase private benefits at the expense of investor welfare \citep{JensenMeckling1976, Musto1999, CarhartKanielMustoReed2002}. Our contribution is to highlight a distinct channel through which agency frictions arise. Specifically, we show that the interaction between convex investor flows and standard fee structures creates an endogenous incentive to increase portfolio volatility, even in the absence of explicit performance fees. Relative to existing work on incentive contracts in asset management \citep{Starks1987, AdmatiPfleiderer1997, HolmstromMilgrom1987}, our framework provides a tractable characterization of how contracts can be designed to control risk-taking directly. Rather than focusing solely on performance-based compensation, we derive a contract that implements a desired risk level as an equilibrium outcome. This approach shifts the emphasis from ex post evaluation of performance to ex ante alignment of incentives.

The closest predecessor to this framework is \citet{basak2007optimal}, who derive optimal portfolio policies for managers facing AUM-linked compensation under convex investor flows in a continuous-time setting with CRRA preferences and benchmark-relative returns. Their analysis fully characterizes the equilibrium volatility distortion: flow convexity generates an option-like payoff that induces managers to tilt toward higher risk. Our contribution is complementary and distinct in three respects. First, we work within a tractable two-period setting that yields a closed-form incentive-compatible fee schedule mapping any investor volatility target to an explicit, implementable compensation level. Continuous-time formulations typically characterize the equilibrium distortion but do not deliver closed-form contract rules directly communicable to practitioners. Second, the tractability of our framework allows us to derive an affine approximation to the exact IC fee schedule and verify numerically that approximation errors are small over empirically relevant ranges, yielding a practical contracting benchmark. Third, our framework allows explicit welfare comparison between the IC contract and a flat-fee benchmark, quantifying the gains from incentive alignment as a function of flow convexity.

Additional related work includes \citet{Starks1987}, who shows that performance incentive fees generate risk-shifting through option-like payoffs; \citet{Carpenter2000}, who demonstrates that option-like compensation more broadly raises managerial risk appetite under nonlinear incentive structures similar to those studied here; \citet{CuocoKaniel2011}, who study equilibrium asset prices in the presence of delegated portfolio management with AUM-linked compensation and document price distortions arising from managerial incentives; and \citet{HuangSialmZhang2011}, who provide empirical evidence that risk shifting in mutual funds is economically significant. Continuous-time principal--agent models for delegated asset management are developed by \citet{OuYang2003}, who characterize optimal contracts under moral hazard; our two-period framework obtains a comparable characterization analytically, trading dynamic completeness for closed-form tractability. \citet{berk2004mutual} predict that positive alpha is competed away by investor flows; our model treats fund skill as given and focuses on the contractual problem conditional on that skill, an approach consistent with the evidence in \citet{carhart1997persistence} that performance persistence is limited but nonzero. \citet{VayanosWoolley2013} study slow-moving capital and flow-induced momentum in a delegated management context; the flow dynamics in our model share the same empirical motivation, though we focus on the contracting problem rather than equilibrium asset prices.

The remainder of the paper is organized as follows. Section~\ref{sec:environment} presents the model and characterizes the incentive-compatible fee schedule. Section~\ref{sec:contract} analyzes the investor's optimal contract design problem. Section~\ref{sec:calibration} provides a calibration of the model. Section~\ref{sec:numerical} presents the numerical illustration. Section~\ref{sec:conclusion} concludes.
