\documentclass[12pt]{article}

%--- Packages ---
\usepackage{amsmath, amsthm, amssymb, amsfonts}
\usepackage{mathtools}
\usepackage{geometry}
\usepackage{booktabs}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{natbib}
\usepackage{setspace}
\usepackage{microtype}
\usepackage{enumitem}
\usepackage{xcolor}
\usepackage{bbm}
\usepackage{dsfont}
\usepackage{algorithm}
\usepackage{algpseudocode}

\geometry{margin=1.25in}
\onehalfspacing

%--- Theorem Environments ---
\newtheorem{theorem}{Theorem}[section]
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{lemma}[theorem]{Lemma}
\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{assumption}[theorem]{Assumption}
\newtheorem{example}[theorem]{Example}
\theoremstyle{remark}
\newtheorem{remark}[theorem]{Remark}

%--- Mathematical Notation ---
\newcommand{\R}{\mathbb{R}}
\newcommand{\Rp}{\mathbb{R}_{+}}
\newcommand{\E}{\mathbb{E}}
\newcommand{\Prob}{\mathbb{P}}
\newcommand{\N}{\mathbb{N}}
\newcommand{\calM}{\mathcal{M}}
\newcommand{\calP}{\mathcal{P}}
\newcommand{\calC}{\mathcal{C}}
\newcommand{\calF}{\mathcal{F}}
\newcommand{\calB}{\mathcal{B}}
\newcommand{\calJ}{\mathcal{J}}
% Notation: \Pi (bold) denotes the SET of all couplings, Pi(mu,nu) = {joint measures with
% marginals mu and nu}. Individual transport plans (elements of this set) are denoted
% pi (lowercase italic). The bold Pi vs lowercase pi distinction mirrors the convention
% in Villani (2003): \Pi is the feasible constraint set; pi is a specific coupling in that set.
% In display equations, Pi(mu,nu) always appears as the constraint set (e.g., inf_{pi in Pi(mu,nu)}),
% while pi appears as a specific element (e.g., int c d pi).
\let\OrigPi\Pi
\renewcommand{\Pi}{\boldsymbol{\OrigPi}}
\newcommand{\Wass}{W_2}
\newcommand{\TV}{\mathrm{TV}}
\newcommand{\supp}{\mathrm{supp}}
\newcommand{\sgn}{\mathrm{sgn}}
\newcommand{\tr}{\mathrm{tr}}
\newcommand{\Id}{\mathrm{Id}}
\DeclareMathOperator*{\argmin}{argmin}
\DeclareMathOperator*{\argmax}{argmax}

%--- Title ---
\title{%
  \textbf{Distributional Debt Capacity:\\
  An Optimal Transport Framework for Capital Structure}%
  \thanks{We thank seminar participants for helpful comments. All errors are our own.}
}

\author{%
  Anonymous Author(s)\\
  \small{[Affiliation Redacted for Review]}
}

\date{\today}

%-------------------------------------------------------------------
\begin{document}
\maketitle
\thispagestyle{empty}

\begin{abstract}
We formulate corporate debt contracting as a Kantorovich linear program: minimize expected deadweight bankruptcy costs over all joint distributions of firm cash flows and promised payments subject to market-clearing constraints. LP duality yields firm-specific contingent shadow prices. Under quadratic cost, Brenier's theorem delivers the optimal contract as the quantile coupling $D^*(X) = F_\nu^{-1}(F_\mu(X))$. An exact result (Proposition~\ref{prop:leverage_wasserstein}) shows that the expected default shortfall at the individual optimal contract equals $W_1(\mu_i,\nu)/2$, where $W_1$ is the 1-Wasserstein ($L^1$) distance between the firm's cash flow quantile function and the capital supply quantile function. This exact formula governs individual leverage via the competitive loan pricing condition. A structural finding is that the same Kantorovich LP with quadratic cost generates \emph{two distinct Wasserstein distances}: $W_2^2(\mu,\nu)$ governs aggregate deadweight costs at the social-planner level; $W_1(\mu_i,\nu)$ governs individual debt capacity. The approximate leverage formula $L_i^* \approx \frac{E_\nu[Y]}{E_{\mu_i}[X]}(1 - W_2(\mu_i,\nu)^2/E_\nu[Y]^2)$ follows after additionally approximating $W_1 \approx W_2^2/E_\nu[Y]$; an $F$-test rejects this functional form ($p=0.046$). This rejection is taken as genuine disconfirmation of the cardinal formula; the Monte Carlo calibration (38\% null rejection rate) is reported as a methodological diagnostic and is not used to rehabilitate the rejected form.

Primary empirical contributions use levels-based Flow of Funds data as the benchmark $\nu$ (theoretically correct; coefficient $-0.219^{***}$, s.e. $0.030$): (1) a deregulation-based IV (LATE coefficient $-0.391$, s.e. $0.098$) on new-issuance rates with four falsification tests, providing causal evidence for the directional mechanism; (2) a shape-component test showing $W_2$ reduces the variance coefficient by 64\% (partial sufficiency); and (3) a first-issuance spread test (1,142 bps, wild cluster bootstrap $p = 0.003$). Two tested predictions distinguish the framework from variance-based models: (P1) leverage responds to supply-side distributional shifts even when firm variance is unchanged; (P2) the benchmark-relative shape component independently predicts leverage beyond mean cash flows. An epistemic status table (Table~5) categorizes each claim as proved, proved-conditional, approximation, or conjecture.
\end{abstract}

\vspace{6pt}
\noindent \textbf{JEL Classification:} G32, G12, C61, D86 \\
\noindent \textbf{Keywords:} Capital structure, optimal transport, Kantorovich duality, Wasserstein distance, debt capacity, corporate finance.

\newpage
\tableofcontents
\newpage

%--- Main Sections ---
\input{sections/introduction}
\input{sections/related_literature}
\input{sections/model}
\input{sections/lp_formulation}
\input{sections/theoretical_results}
\input{sections/empirical}
\input{sections/conclusion}

%--- Appendix ---
\appendix
\input{appendix/proofs}
\input{appendix/data}

%--- Bibliography ---
\bibliographystyle{plainnat}
\bibliography{references}

\end{document}
